### 2015-06-19 reports/paper/prior.tex
thesis update

The Kalman filter update equations are:
\begin{eqnarray}
\hat{x}_k^- & = & A\hat{x}_{k-1} + Bu_k\\
P_k^- & = & AP_{k-1}A^T + Q\\
K_k & = & P_k^- H^T(HP_k^-H^T+R)^{-1}\\
\hat{x}_k & = & \hat{x}_k^- + K_k(z_k-H\hat{x}_k^-) \\
P_k & = & (1-K_kH)P_k^-
\end{eqnarray}
where:
\begin{itemize}
\item $\hat{x}_k^-$ is
\item $P_k^-$ is
\item $K_k$ is
\item $hat{x}_k$ is
\item $P_k$ is
\end{itemize}

>>>>

The Kalman filter has a prdict step:
\begin{eqnarray}
\hat{x}_{k+1}^- & = &F_k \hat{x}_k + B_ku_k\\
P_{k+1}^- & = & F_kP_kF_k^T + Q_k\\
\end{eqnarray}
and an update step:
\begin{eqnarray}
y_k & = & z_k - H_k\hat{x}_k^-\\
S_k & = & H_kP_k^-H_k^T + R_k \\
K_k & = & P_k^-H_k^TS_k^{-1}\\
\hat{x}_k & = & \hat{x}_k^- + K_ky\\
P_k & = & (I-K_kH_k)P_k^-\\
\end{eqnarray}
where:
\begin{itemize}
\item $x$ is the state variable
\item $P$ is the covariance on the state variable $x$
\item $F_k \hat{x}_k + B_k u_k$ describes the station transition form time $k$ to $k+1$. The Kalman filter is a general framework which allows not only tracking but also controlling the object. I these situations $u_k$ is the control input and $B$ describes the control input model. For our application, we are only tracking and not controlling the movement, $B_ku_k = 0$.
\item $z$ is the measurement.
\item $y$ is the residue in the measurement sapce. 
\item $H$ is the measurement function that transforms from state space to measurement space.
\item $R$ is the measurement noise matrix that models sensor noise as a covariance matrix
\item $Q$ is the unmodeled noise in the process.
\end{itemize}
